Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-04-29 WorkSpace/Paper/Paper.tex
fixed paper typos

\noindent\textbf{Linear Congruential}:
\begin{itemize}
    \item A linear congruential generator is a PRNG that represents an "additive  congruential  method", with foundations in improving upon "unsatisfactory" tests with entropy in fibonacci sequences. \cite{10.1145/321008.321019}
\end{itemize}
Notes:
\begin{itemize}
    \item The generator is not sensitive to the choice of c, 
as long as it is relatively prime to the modulus 
(e.g. if m is a power of 2, then c must be odd), 
so the value c=1 is commonly chosen.
    \item If c = 0, the generator is often called a multiplicative
congruential generator (MCG), or Lehmer RNG (which is used for our implementation). If c ≠ 0, the
method is called a mixed congruential generator.
    \item Parameters were chosen based on $2^32$ numbers in table 2 of the article "Tables of linear congruential generators of different sizes and good lattice structure." \cite{LEcuyer1999TablesOL}
\end{itemize}

@@

Given an enumerated set, $\mathbb{N}$,
where $prng$ is the chosen PRNG, $S_n$ is $n$th seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
$\mathbb{X}_n$ represents an enumerated set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is derived from a different seed. $\mathbb{Y}_n$ represents a set containing $n$ sets of $k$th values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \mapsto \mathbb{Y}_n$. $P$ a predictor function that represents a convolutional neural network, which takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on back-propagation due to previous predictions, thus using supervised learning to build a regression model.

@@

Other than slight ambiguity in errors, we realize that our PRNG methods might not be perfect implementations. Some generators have tight tolerances for parameters and algorithmic behaviors. While we believe that our implementations are sound, they could be checked and improved upon by using tests of statistical randomnesses, such as the National Institute of Standards and Technology (NIST) provides. 
Different seeding methods could also provide different results, given that our seeding method was relatively linear and weak in design.

>>>>

\noindent\textbf{Linear Congruential}:
\begin{itemize}
    \item A linear congruential generator is a PRNG that represents an "additive congruential method", with foundations in improving upon "unsatisfactory" tests with entropy in fibonacci sequences. \cite{10.1145/321008.321019}
\end{itemize}
Notes:
\begin{itemize}
    \item The generator is not sensitive to the choice of c, 
as long as it is relatively prime to the modulus 
(e.g. if m is a power of 2, then c must be odd), 
so the value c=1 is commonly chosen.
    \item If c = 0, the generator is often called a multiplicative
congruential generator (MCG), or Lehmer RNG (which is used for our implementation). If c $\neq$ 0, the
method is called a mixed congruential generator.
    \item Parameters were chosen based on $2^32$ numbers in table 2 of the article "Tables of linear congruential generators of different sizes and good lattice structure." \cite{LEcuyer1999TablesOL}
\end{itemize}

@@

Given an enumerated set, $\mathbb{N}$,
where $prng$ is the chosen PRNG, $S_n$ is $n$th seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
$\mathbb{X}_n$ represents an enumerated set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is derived from a different seed. $\mathbb{Y}_n$ represents a set containing $n$ sets of $k$th values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \mapsto \mathbb{Y}_n$. $P$ is a predictor function that represents a convolutional neural network, which takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on back-propagation due to previous predictions, thus using supervised learning to build a regression model.

@@

Other than slight ambiguity in errors, we realize that our PRNG methods might not be perfect implementations. Some generators have tight tolerances for parameters and algorithmic behaviors. While we believe that our implementations are sound, they could be checked and improved upon by using tests of statistical randomnesses, like the National Institute of Standards and Technology (NIST) provides. 
Different seeding methods could also provide different results, given that our seeding method was relatively linear and weak in design.
